Gozde and Liora extension

### 2015-04-30 extension.Rmd

# Run necessary packages and load data (Source: Arzheimer dataverse)

@@

Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power.

>>>>

Run necessary packages and load data (Source: Arzheimer dataverse)

@@

Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power given the level of concentration of events in the upper probabilities area in the plot.
